### 2021-11-09 response/response.tex

  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications. In a particular application that uses the switching operation of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage. As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field. This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage. Based on these available nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers great potential to realize advanced nanoelectronic devices. Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
  }
\end{itemize}

\subsubsection*{Comment 4 -
\color{RoyalBlue} The quantum Quantum Hall effect requires high mobility samples. In these samples, the structure of the disorder is usually complicated and combines both short-length potentials of impurities and long-length electrostatic inhomogeneities. The interplay of these components of disorder opens exciting questions about the transport properties of 2DEGs. What is the structure of disorder considered in the present manuscript and hidden in the notations for Vimp? What are the conditions for validity of eq. (15)?
}

We thank the reviewer for raising this important question. In our previous manuscript, we have presented the detailed derivation of Eq.~[15] with a discusssion on models of disorder under the Appendix C. However we will discuss on our selection of disorder model and approximations made to derive the Eq.~[15] here as well.

@@

We modeled the effect caused by impurities in the considered system as a single perturbation potential. Analyzing the electric propeties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment. Therefore, in this study we consider on the statistically averaged propeties of 2DEG over impurity configurations. In addition, we consider only the our considering static disorder corresponds to the situation in which the electrons scatter elastically. First, we adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the considering system and we approximate this into a Gaussian white noise.

Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly localized impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$. Thus, we can describe the scattering potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
\begin{equation} \label{eq:1}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \upsilon (\vb{r}-\vb{r}_i).
\end{equation}
Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average. This model is characterized by the following two equations \cite{akkermans10}
\begin{subequations}
\begin{equation} \label{eq:2}
  \expval{\upsilon(\vb{r})}_{imp} =0,
\end{equation}
\begin{equation} \label{eq:3}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
\end{equation}
\end{subequations}
where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$. In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$. Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
\begin{equation} \label{eq:4}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
\end{equation}
where $\Upsilon_{imp}^2$ is a constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
\begin{equation} \label{eq:5}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
\end{equation}

@@

Then we calculate the Floquet-Fermi golden rule for a dressed quantum Hall system using this perturbative impurity potential. In the derivation we have defined the $V_{imp}$ value which is constant in moemntum space. It is a propety of Gaussian white noise impurity distribution \cite{akkermans10,wackerl20}. However, throughout the derivation we use only the first order contribution (Born approximation) of the impurity potential. All the detailed step for the derivation of the Floquet-Fermi golden rule for a dressed quantum Hall system are included in Appendix C.

Since previous studies on Floquet-Drude consuctivity \cite{wackerl20}, and magnetotransport propeties in dressed qunatum Hall systems \cite{dini16} have  used this perticular Gaussian white noise potential, we also selected this pertucular impurity model to describe our system. This open a path to compare our analytical outcomes with these previous models. As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the magnetotransport properties of dressed qunatum Hall system would be an interesting future research possibility.

### 2021-11-09 response/response.tex

\subsubsection*{Comment 5 -
\color{RoyalBlue} If continuous illumination is applied to an electron system, the system will heat indefinitely. The distribution function is stabilized when the electron-electron and electron-phonon scattering mechanisms are included. What are the conditions of validity for eqs. (33-34)? The deviations of the distribution function from its equilibrium result in effects that can significantly overcome the equilibrium contributions, see Dmitriev et al, Phys. Rev. B 80, 165327 (2009). However, to capture these effects, a treatment within Floquet-Drude formalism is insufficient and a complete quantum kinetic equation has to be analyzed. Can the authors argue why their results still present some interest to the community even if they potentially disregard more significant contributions?
}

This is a good, valid question. First, we discuss the validity of the Eq.~[33] and Eqq.~[34]. In our analysis we have derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31]. Then we selected an special scenario where we assumed that the system is under low temperature limit. Since previous theoritical studies on magnetotransport propeties of 2DEG quantum Hall systems were derived under this assumption, we selected this conditions to provide a better comparison with their outcomes. In addition, as mentioned in previous experimental studies on SdH oscillations \cite{zudov03,mani02,arapov02} in 2DEG undressed quantum Hall systems with increasing tempurature, we can identify the decaying behaviour of SdH oscillations. Therefore, if we need to maintain a good oscillator behavior we need to work in low temperatures. Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, we have extend our general derivation in given Eq.~[31] into a simple expression for low temperature case. On the other hand, under the off-resonant condition, absorption of photons is avoided, and we can choose the the Fermi-Dirac distribution as our partical distribution function in Eq.~[31] as given in Eq.~[33]. Under low temperature assumption, we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy as given mentioned in the Eq.~[34]. Applying these two conditions, we can simplify our derivation into new expression that can be compared with previous studies on magnetotransport in dressed quantum Hall systems.

Yes, it is true that when we consider the experimental observations of a qunatum Hall system a strong dressing field can increase the temperature of the sample. However, as mentioned in previous study by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, we can maintain low temperature by applying narroaw pulses of a strong dressing field to observe the discussed phenomena.

Although we have extend our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoritical model into different type of partical distribution functions. As discussed by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion need to address the changes in distribution functions in our derived general longitudinal conductivity formula and this would be an interesting extension to our study.

\subsubsection*{Comment 6 -
\color{RoyalBlue} The authors presented the results for the conductivity tensor's xx- and yy-components. They seem to be identical, apart of a dimensional factor $(eB)^2$ in the denominator. The equality of these two components is expected for isotropic systems. Does the polarization of the electromagnetic field break the isotropy? Do the two components of the conductivity remain equal even for an arbitrary direction of a linearly polarized field? Is there a non-Hall contribution to the xy-component?
}

### 2021-11-10 response/response.tex

Yes, it is true that when we consider the experimental observations of a qunatum Hall system a strong dressing field can increase the temperature of the sample. However, as mentioned in previous study by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, we can maintain low temperature by applying narroaw pulses of a strong dressing field to observe the discussed phenomena.

Although we have extend our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoritical model into different type of partical distribution functions. As discussed by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion need to address the changes in distribution functions in our derived general longitudinal conductivity formula and this would be an interesting extension to our study.

\subsubsection*{Comment 6 -
\color{RoyalBlue} The authors presented the results for the conductivity tensor's xx- and yy-components. They seem to be identical, apart of a dimensional factor $(eB)^2$ in the denominator. The equality of these two components is expected for isotropic systems. Does the polarization of the electromagnetic field break the isotropy? Do the two components of the conductivity remain equal even for an arbitrary direction of a linearly polarized field? Is there a non-Hall contribution to the xy-component?
}

For analysing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}. The Floquet-Drude conductivity formula was only developed for the diogonal components of the conductivity tensor of the considering system. In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analysed the dressing field effect on two diogonal components of the conductivity tensor.

As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the qunatum state of the consideirng system and creates novel states called Floquet states. The propeties of these states are depends on the characteristics of applied dressing field. Therefore, the polarization method also change the behavior of the Floquet states.
These polarization dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields. In addition, they have mentioned the impact on the direction of the linearly polarization dressing field and this will break the isotropy behaviour of the longitudinal conductivities in the consideirng system.

We also followed the same formalism of Floquet states for 2DEG quantum Hall systems. In our work also we were able to identify that the applied dressing field's polarization direction can be effect the magnitude of the longitudinal conductivity component. A detailed derivation of these two longitudinal conductivity component's current operators are given in Appendix D. If we applied a arbitary directional polarized dressing field, we can derive a expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with same steps in this analysis. This would change the amplitude of the considering dressing field ($E$) in each direction. However, now there will be a new conponent in parallel to the considering conductivity component and we need to solve the Schrödinger equation with the modified Hamiltonian in Eq.~[2] for the new system with these changes.
However in our analysis, our main objective was to identify the manipulation capabilities of SdH oscillations using dressing field intensity. In addition, we only consider the longitudinal components in this analysis by extending the Floquet-Drude conductivity formula that derived only for the diogonal components in conductivity tensor. Therefore we are unable to predict the off-diogonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.

### 2021-11-10 response/response.tex

  In our work, we analysed the 2DEG quantum Hall system with high-intensity dressing field which does not contribute to the energy exchange between a high-frequency dressing field and electrons. Therefore we have assumed the applied electromagnetic radiation as a purely dressing field. There are two possible absorbtion mechanism in 2DEG quantum Hall system namely electron transitions bewtween distinct Landau levels and electron transitions between distinct states of a same broadened Landau level. To avoid these absorbtions we have tuned the dressing field to a high frequency in our system under the analysis. Furthermore due to high intensity dressing field, it will restructure the entire electronic states of the conventinal 2DEG quantum Hall systems. We have address these modifications throuth the Floquet theory. However, the MIROs models \cite{durst03,dmitriev03} are based on low frequecy case where the system is able to absorb low frequency photons from the field.
\end{itemize}

Examine above mentioned points, we can clearly identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two particular natures of the magnetotransport properties. However, we identify that it is crusial to acknowledge these well-defined findings in MIROs and the their relatioship to the our considered system. We have added this clarification in the manuscript.
  \item Section I - fifth paragraph (page 1):\\
  {\color{Maroon}
  In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
  Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport. Recently, an experimental research on the effect of microwave illumination of 2DEG systems revealed microwave induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
  This inspired investigations on theoretical description of MIROs and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These analytical formalisms provide a good explanation of the experimental characteristics of MIROs. However, these experimental and theoretical works have been linked to the photon absorbtion from low-frequecy (microwave) fields. In contrast to that, high-frequency external illumination on 2DEG quantum Hall system need to be study as a purely dressing (nonabsorbable) field.
  The impacts induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be descriped by a nonabsorbtion mechanism and it has escaped the researchers’ attention before.
  Then, lately Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems for high-frequency case. However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
  }
  \item Section VI - fifth paragraph (page 8):\\
  {\color{Maroon}
  By comparing the theoritical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on magnetoresistance of 2DEG qunatum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are repetition of the Shubnikov–de Haas(SdH) oscillations.
  As observed in the experimental work by Caviglia \textit{et al.} \cite{caviglia10}, SdH oscillations period is only depend on the perpendicular component of the applied magnetic field.
  Therefore, we can identify that many experiments done in low temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with different type of 2DEG has been oberved these SdH oscillations against applied magnetic field.
  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the consdiering system.
  Therefore we can achieve the same oscillation behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage. Due to the change of the gate volatge applied to the system will modify the Fermi level of the system.
  Since the Landau level energy is only depend on the cyclotron frequency, this will generate the same SdH oscillations against gate volatage.
  This osillating behavior with applied gate volatge has been observed in experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature. With comparing these empirical observations with our results given in Fig[4], we can easly identify that our oscillations are also shows the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value. Furthermore, when we increase the gate volatge, the Fermi level of the system get increased. This will locate to the the Fermi level on higher order Landau levels. As illustrated in Fig.~[4], this will result a higher conductivity peak value at higher order Landau level. This same behaviour also observed in the experimental observations presented in Ref. \cite{wakabayashi78} as well. However, in our analysis we have analytically explained the controllability of these conductivity regions using a dressing field.
  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered a number of remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems. However these experiments and theoritical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorbtion from the applied low-frequency field.
  It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field. In our case, the applied dressing field is in off-resonant range and that will only change the the broadening of Landau levels and avoid any contribution towards the photon absorbtions. This will clearly describe the crusial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems. Therefore our approach can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
  }

@@

We also followed the same formalism of Floquet states for 2DEG quantum Hall systems. In our work also we were able to identify that the applied dressing field's polarization direction can be effect the magnitude of the longitudinal conductivity component. A detailed derivation of these two longitudinal conductivity component's current operators are given in Appendix D. If we applied a arbitary directional polarized dressing field, we can derive a expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with same steps in this analysis. This would change the amplitude of the considering dressing field ($E$) in each direction. However, now there will be a new conponent in parallel to the considering conductivity component and we need to solve the Schrödinger equation with the modified Hamiltonian in Eq.~[2] for the new system with these changes.
However in our analysis, our main objective was to identify the manipulation capabilities of SdH oscillations using dressing field intensity. In addition, we only consider the longitudinal components in this analysis by extending the Floquet-Drude conductivity formula that derived only for the diogonal components in conductivity tensor. Therefore we are unable to predict the off-diogonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.

\subsection*{Response to the comments of Reviewer 2}

We would like to thank the reviewer for his/her insightful comments our work. To address your comments, we had to add new materials and reorganize our text. As a result we have been able to considerably improve our discussion on the underlying assumptions and corresponding physical significance of our analysis. We hence believe that both the presentation and scientific content of this manuscript is of a much higher quality than our previous submission. We hope our response, and the corresponding changes we incorporated to the manuscript would be sufficient to clarify the issues raised.

\subsubsection*{Comment 1 -
\color{RoyalBlue} The paper is very low on comparison with experiments, for which there is a large amount of data available for the zero radiation case. I would like to see detailed analysis of how Figs 4 and 5 compare with available
experimental data. Without this addition, physical relevance of such
detailed calculations is questionable.
}

We thank the reviewer for pointing out the importance of this fact. To overcome this shortage of discussion we made a detailed analysis on our results against the undressed 2DEG quantum Hall system behavior. We have inserted this discussion into the our manuscript under Section VI.

\begin{itemize}
  \item Section VI - fifth paragraph (page 8):\\
  {\color{Maroon}
  By comparing the theoritical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on magnetoresistance of 2DEG qunatum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are repetition of the Shubnikov–de Haas(SdH) oscillations.
  As observed in the experimental work by Caviglia \textit{et al.} \cite{caviglia10}, SdH oscillations period is only depend on the perpendicular component of the applied magnetic field.
  Therefore, we can identify that many experiments done in low temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with different type of 2DEG has been oberved these SdH oscillations against applied magnetic field.
  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the consdiering system.
  Therefore we can achieve the same oscillation behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage. Due to the change of the gate volatge applied to the system will modify the Fermi level of the system.
  Since the Landau level energy is only depend on the cyclotron frequency, this will generate the same SdH oscillations against gate volatage.
  This osillating behavior with applied gate volatge has been observed in experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature. With comparing these empirical observations with our results given in Fig[4], we can easly identify that our oscillations are also shows the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value. Furthermore, when we increase the gate volatge, the Fermi level of the system get increased. This will locate to the the Fermi level on higher order Landau levels. As illustrated in Fig.~[4], this will result a higher conductivity peak value at higher order Landau level. This same behaviour also observed in the experimental observations presented in Ref. \cite{wakabayashi78} as well. However, in our analysis we have analytically explained the controllability of these conductivity regions using a dressing field.
  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered a number of remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems. However these experiments and theoritical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorbtion from the applied low-frequency field.
  It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field. In our case, the applied dressing field is in off-resonant range and that will only change the the broadening of Landau levels and avoid any contribution towards the photon absorbtions. This will clearly describe the crusial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems. Therefore our approach can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
  }
\end{itemize}

### 2021-11-10 response/response.tex

\subsubsection*{Comment 2 -
\color{RoyalBlue} In the presence of disorder, Anderson localization and topologically protected edge modes are dominant considerations when calculating DC transport coefficients. How are these factors taken into account?
}

\subsubsection*{Comment 3 -
\color{RoyalBlue} Can the authors reproduce the quantized Hall conductance of filled Landau levels in the presence of disorder? Please discuss.
}

\subsubsection*{Comment 4 -
\color{RoyalBlue} The way some previous works are cited is disappointing. Example from page 8: “Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.” This is not informative. Where, specifically, did results from earlier works fall short of reality, which have been better addressed in this work?
}

\subsubsection*{Comment 5 -
\color{RoyalBlue} Adding some physical insight into the remarkable observation of radiation-induced narrowing of lineshapes (Figs 4, 5) will help elevate
this work.
}

We agree with the reviewer that a discussion on our theoritical results and their physical significance into modern nanoelectronic devices is a vital requirement. We have added a new Section VII to overcome the above mentioned deficiency of our manuscript. The total content of the section is given below,

\begin{itemize}
  \item Section VII (page 8):\\
  {\color{Maroon}
  \subsection*{Physical significance of the outcomes}
